A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-25 sections/Related.tex
RW Ordered contexts

\paragraph{Ordered Contexts in Type Inference}
Gundry et al.~\cite{gundry2010type}

>>>>

\paragraph{Ordered Contexts in Type Inference}
Gundry et al.~\cite{gundry2010type} revisit algorithm $\mathcal{W}$ and
propose a new unification algorithm with the help of ordered contexts.
Similar to DK's algorithm, information of meta variables flow from input contexts to output contexts.
Not surprisingly, its information increase relation acts as a similar role to DK's context extension.
Our algorithm, in contrast,
eliminates the use of output contexts and their variable solution records ($\al = \tau$),
simplifying the information propagation process through immediate substitution
by collecting all the judgments in a single worklist.
